Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
new table for C++ us vs them. Much simpler

% ---------------- C++ table (UM vs Others)--------------------------
\begin{table}[htbp]
\centering
{\small
\caption{C++ (Our Implementation vs. Dextool)}
\label{tab:table_cpp2}
\begin{tabularx}{\columnwidth}{X|crr|crr}
\hline
        & \multicolumn{3}{c|}{Comby}  & \multicolumn{3}{c}{Dextool} \\ 
Project & $\frac{killed}{total}$ & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & $\frac{killed}{total}$ & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\[1ex]\midrule
 ompl & $\frac{41}{564}$ & 0.07 & 40\% & $\frac{23}{278}$ & 0.08 & N/A \\[1ex]
%\multirow{3}{*}{\small libgraphqlparser} & Comby & 116 & 15 & 0.89 & 20\% \\ \cline{2-6}
%    & Dextool & 50 & 2 & 0.96 & N/A \\ \hline
%\multirow{3}{*}{\small rethinkdb\_rebirth} & Comby & 49 & 443 & 0.10 & 20\% \\ \cline{2-6}
%    & Dextool & 9 & 16 & 0.36 & N/A \\ \hline

%\multirow{3}{*}{\small xoreos} & Comby & 33 & 2247 & 0.01 & 10\% \\ \cline{2-6}
%    & Dextool & 8 & 406 & 0.02 & N/A \\ \hline
%\multirow{3}{*}{\small libxmljs}  & Comby & 507 & 283 & 0.64 & 10\% \\ \cline{2-6}
%    & Dextool & 383 & 447 & 0.46 & N/A \\ \hline
%\multirow{3}{*}{\small tiny-differentiable-simulator} & Comby & 32 & 738 & 0.04 & 0\% \\ \cline{2-6}
%    & Dextool & 13 & 48 & 0.21 & N/A\\ \hline
%    
%\multirow{9}{*}{Overall}\multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.29 & 16.67\% \\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Median} & 0.09 & 15.00\% \\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.37 & 13.66\% \\\cline{2-6}
%
% & \multirow{3}{*}{Dextool} & \multicolumn{2}{c|}{Mean} & 0.33 & N/A\\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Median} & 0.29 & N/A \\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.38 & N/A \\ \hline
\end{tabularx}
}
\end{table}

>>>>

% ---------------- C++ table (UM vs Others)--------------------------
\begin{table}[htbp]
\centering
{\small
\caption{C++ (Our Implementation vs. Dextool)}
\label{tab:table_cpp2}
\begin{tabularx}{\columnwidth}{X|crr|crr}
\hline
        & \multicolumn{3}{c|}{Comby}  & \multicolumn{3}{c}{Dextool} \\ 
Project & Mutants & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & $\frac{killed}{total}$ & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\[1ex]\midrule
 ompl &  564 & 0.07 & 40\% & 278 & 0.08 & N/A \\
%\multirow{3}{*}{\small libgraphqlparser} & Comby & 116 & 15 & 0.89 & 20\% \\ \cline{2-6}
%    & Dextool & 50 & 2 & 0.96 & N/A \\ \hline
%\multirow{3}{*}{\small rethinkdb\_rebirth} & Comby & 49 & 443 & 0.10 & 20\% \\ \cline{2-6}
%    & Dextool & 9 & 16 & 0.36 & N/A \\ \hline

%\multirow{3}{*}{\small xoreos} & Comby & 33 & 2247 & 0.01 & 10\% \\ \cline{2-6}
%    & Dextool & 8 & 406 & 0.02 & N/A \\ \hline
%\multirow{3}{*}{\small libxmljs}  & Comby & 507 & 283 & 0.64 & 10\% \\ \cline{2-6}
%    & Dextool & 383 & 447 & 0.46 & N/A \\ \hline
%\multirow{3}{*}{\small tiny-differentiable-simulator} & Comby & 32 & 738 & 0.04 & 0\% \\ \cline{2-6}
%    & Dextool & 13 & 48 & 0.21 & N/A\\ \hline
%    
%\multirow{9}{*}{Overall}\multirow{3}{*}{Comby} & \multicolumn{2}{c|}{Mean} & 0.29 & 16.67\% \\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Median} & 0.09 & 15.00\% \\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.37 & 13.66\% \\\cline{2-6}
%
% & \multirow{3}{*}{Dextool} & \multicolumn{2}{c|}{Mean} & 0.33 & N/A\\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Median} & 0.29 & N/A \\\cline{3-6}
%    &   &  \multicolumn{2}{c|}{Std. Dev} & 0.38 & N/A \\ \hline
\textbf{Mean}   & FIXME & 0.29 & 16.67\% & FIXME & 0.33 & N/A\\
\textbf{Std. Dev} & FIXME & 0.37 & 13.66\%   & FIXME & 0.38 & N/A \\\bottomrule
\end{tabularx}}
\end{table}
